---
output: github_document
---
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
  
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# teamtools

The goal of teamtools is to facilitate team work and content organisation 
if the following directory structure is present:
```{bash, eval = FALSE}
team
|- project 1
|   |- repository 1
|   |- repository 2
|- project 2
    |- repository 3
    |- repository 4
```

Such a project structure is common for teams working on BitBucket. Every
repository is technically an independent git repo. If you use another remote
git client, you can anyways organize different repos in projects under a team
root. Note that a team root is characterized by a directory having a `.team` 
file.

# README structuring

teamtools suggests that a repository's description is stored in `.description`. 
This may be used in the Rmd README by placing 
` r teamtools::read_local_description()` (enclosed in backticks) to import 
anywhere in the description into the README. You can use markdown
syntax in the `.description` as this will be placed into the README as is before
compiled with Pandoc.

The following descritpion was generated with the command mentioned above:

`r teamtools::read_local_description()`


***

The advantage of this approach is that these short descriptions can be 
accessed easily programmatically, much easier than if we had to parse 
a README and extract the first paragraph or something like that. 
You can easily retrieve all descriptions from all repos in all projects with
```{r, eval = FALSE}
teamtools::read_description_files()
```

Note taht this works if your current working directory is *any* directory
under the team root.
